Macro Impacts

### 2016-07-11 Macro Impacts Revised.tex
Woah dude cool stuff man

\Xi&\geq\p{\f{K^2}{\lambda+2\mu}}\p{\f{4\pi}{3\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

\Xi&<\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

\dot \theta&=\f{p v^2}{r^2}

@@

1&=\f{r\dot r}{\sqrt{v^2r^2-p^2v^4}}

@@

s+C&=\int\f{r\diff r}{\sqrt{v^2r^2-p^2v^4}}\,.

@@

r(s)&=r_0^{\f{\alpha}{1+\alpha}}v_0^{\f{1}{1+\alpha}}(p^2+(C+s)^2(1+\alpha)^2)^{\f{1}{2(1+\alpha)}}\,.

@@

\theta(s)&=\f{1}{1+\alpha}\arctan\ps{\f{1+\alpha}{p}(C+s)}+\theta_0

@@

WOAH!
\end{document}

>>>>

\Xi&\geq\f{16}{9}\p{\f{K^2}{\lambda+2\mu}}\p{\f{\pi}{\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

\Xi&<\f{9}{4}\p{\f{K^2}{\lambda+2\mu}}\p{\f{\pi}{\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

\dot \theta&=\pm\f{p v^2}{r^2}

@@

1&=\pm\f{r\dot r}{\sqrt{v^2r^2-p^2v^4}}

@@

s+C&=\pm\int\f{r\diff r}{\sqrt{v^2r^2-p^2v^4}}\,.

@@

r(s,\alpha)&=r_0^{\f{\alpha}{1+\alpha}}v_0^{\f{1}{1+\alpha}}(p^2+(C+s)^2(1+\alpha)^2)^{\f{1}{2(1+\alpha)}}\,.

@@

\theta(s,\alpha)&=\f{1}{1+\alpha}\arctan\ps{\f{1+\alpha}{p}(C+s)}+\theta_0

@@

WOAH! We expect straight lines when $\alpha=0$. Let's check:
r(s,0)&=v_0\sqrt{p^2+(C+s)^2}\,,\\
\theta(s,0)&=\arctan\ps{\f{C+s}{p}}+\theta_0
Setting $\theta_0$ to zero reveals the equation for a vertical line. Thus, adding $\theta_0$ rotates the line, and $p$ sets the initial distance from the origin.
Now we consider the realistic velocity distribution $v(r)=a^2-b^2r^2$. Proper application of mathematica to the above formulas reveals
r(s)&=\f{a\sqrt{b^2-2be^{2ab(s+C)}+e^{4ab(s+C)}+4a^2b^4p^2}}{b\sqrt{b^2+2be^{2ab(s+C)}+e^{4ab(s+C)}+4a^2b^4p^2}}\,,\\
\theta(s)&=\arctan\ps{\f{-b^2+e^{4ab(s+C)}+4a^2b^4p^2}{4ab^3p}}+\theta_0
Qualitatively, these appear to be arcs of circles which touch the boundary $r=\f ab$ at right angles. It would be nice to double check this. If that is the case, then this is an instance of rays tracing out geodesics in the Poincare disk.

We now want to calculate the distribution of rays about the perimeter of a circle. In essence, we want to know $\diff\theta(R_{\te{earth}})$ as a function of $p$ and $\theta_0$. First we pick a point $p$ and direction $\psi$. we now parametrize all ray trajectories passing through this point by $\psi$. We now fix a $\psi$ and add to it $\delta\psi$, chosen small enough so that the two corresponding trajectories are close together. We then calculate $\delta\theta(R_{\te{earth}})$, the angular distance between the two rays as measured from the origin when they are at the radius of the earth.
\\\\
TO DO: Parametrize the rays through a point. Get the final parameter $s(R_{\te{earth}})$ as a function of the angle through the point. Then figure out how a small change in the initial angle changes the final angle. Get an approximate model for the velocity field through the earth.

%\pagebreak
%Meeting Agenda: Found bounds for $\Xi$. We need to map intensity to the surface - how? Do we make a generous over estimate again? If so, how should we approach it?
\end{document}
